Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-16 fib2.tex
more pictures, more words

\begin{center}
\includegraphics[]{pic-interaction.pdf}
\end{center}

>>>>

We can think of braids acting on states in a Schrodinger picture,
or alternatively, elements of the mapping class group acting on
observables in a Heisenberg picture:
\begin{center}
\includegraphics[]{pic-interaction.pdf}
\end{center}

We would hope that the groups $B_n$ and $MCG(D_n)$ are
isomorphic, and this is indeed the case~\cite{Kassel2010}.
One can see this as follows. Dragging the space $D_n$ along
a braid creates a deformation, the end point of which is a
homeomorphism in $MCG(D_n).$ Going the other direction,
given $f\in MCG(D_n)$ and a curve diagram $c,$ we think of
pulling the ends of $fc$, thereby moving (braiding) the holes,
until we are back at the original curve $c.$
